
% --- LaTeX CV Template - S. Venkatraman ---

% Set document class and font size
\documentclass[letterpaper, 11pt]{article}
\usepackage[utf8]{inputenc}

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings ---

% Set page margins
\usepackage[left=1in, right=1in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.15}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

% Remove page numbering
\pagenumbering{gobble}

% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
\noindent{\Huge{Lucy Hao}
\hfill{\it\footnotesize Updated \today}}

% --- Contact information and other items ---
\vspace{0.5cm} 
\noindent{\textbf{Email}: lhao03@student.ubc.ca \hspace{0.4in} \textbf{Phone}: +1 403 401 3096 \hspace{0.4in} \textbf{Citizenship}: USA, Canada}

% --- Start the two-column table storing the main content ---

% Set spacing between columns
\setlength{\tabcolsep}{8pt}

% Set the width of each column
\begin{longtable}{p{1.3in}p{4.8in}}

% --- Section: Research interests ---
\nohyphens{\color{Blue}{Research Interests}}
& programming languages; chemical biology; computer science education; computational life sciences, computer systems software \\
& \\

% --- Section: Education ---
\color{Blue}{Education} 
& \textbf{University of British Columbia} \hfill Vancouver, British Columbia \\
& B.Sc. Combined Computer Science and Chemistry \hfill Sep. 2019 -- Dec. 2024 \\
& {\it GPA: 83\%} \\
& \\

& \textbf{Selected coursework}
\begin{itemize}[noitemsep,leftmargin=*]
\item \underline{CPSC 436A}: Operating Systems Design and Implementation
\item \underline{CHEM 330}: Advanced Organic Chemistry
\item \underline{CPSC 539B}: Topics in Programming Languages
\item \underline{MICB 306}: Molecular Virology
\end{itemize} \\

% --- Section: Awards, scholarships, etc. ---
% --- Note: section title is spread over two lines ---
{\color{Blue}{Honours and}} 
& Biotalent Canada Student Work Placement Program Grant (\$5,000) \hfill 2021\\
{\color{Blue}{Scholarships}} 
& Alexander Rutherford High School Achievement Scholarship (\$2,500)\hfill 2019 \\
& \\

% --- Section: Publications ---
\nohyphens{\color{Blue}{Publications}} 
& \textbf{Automated medical chart review for breast cancer outcomes research: a novel natural language processing extraction system.} \\
& Chen, Y., Hao, L., Zou, V.Z., Hollander, Z., Ng, R.T., Isaac, K.V. \\
& \textit{BMC Med Res Methodol 22, 136 (2022).} \\
& \\

% --- Section: Research experience ---
\nohyphens{\color{Blue}{Research Experience}} 
& \textbf{PROOF Centre, UBC} \\
& Advisors: Prof. Raymond Ng, Prof. Dr. Kathryn Isaac \hfill Jan. 2021 -- May 2021 \\
& Undergraduate Research Intern \\
& \\

% --- Section: Teaching experience ---
{\color{Blue}{Teaching Experience}} 
& \textbf{Systematic Program Design (CPSC 110)} \hfill Winter 2022 \\
& \textit{Current} \\
& \\

& \textbf{Systematic Program Design (CPSC 110)} \hfill Winter 2021 \\
& \textit{Average student rating: 90\%.} \\
& \\

& \textbf{Software Construction (CPSC 210)} \hfill Summer 2021 \\
& \textit{Average student rating: 100\%.} \\
& \\

& \textbf{Software Construction (CPSC 210)} \hfill Winter 2020 \\
& \textit{Average student rating: 80\%.} \\
& \\

% --- Section: Industry experience ---

{\color{Blue}{Industry Experience}} 
& {\textbf{Capital One,}} TIP \hfill New York City, New York\\
& Software Engineering Intern \hfill Summer 2022 \\
& \\
 
& {\textbf{Microsoft,}} Garage \hfill Vancouver, British Columbia\\
& Software Engineering Intern \hfill Summer 2021 \\
& \\

% --- Section: Talks and tutorials ---

{\color{Blue}{Talks and tutorials}} 
& \textbf{Intersections of Technology Panel} \hfill Jan. 2022 \\
& StarHacks II \\
& \\

& \textbf{Intro to Technical Interviews} \hfill Nov. 2021 \\
& HackCamp \\
& \\

& \textbf{Pursuing a Successful Career in CS + Technology} \hfill Jul. 2021 \\
& Hacking 4 Community \\
& \\

& \textbf{Intro to NLP} \hfill Jun. 2021 \\
& Hydrangea Hacks \\
& \\

& \textbf{Intro to Git and GitHub} \hfill Jun. 2021 \\
& Citro Hacks \\
& \\

& \textbf{Computers and Technology Panel} \hfill May 2021 \\
& Joy to Job \\
& \\

& \textbf{Intro to Git and GitHub and Intro to Python} \hfill Jan. 2021 \\
& StarHacks I \\
& \\

% --- Section: Various skills (programming, software, languages, etc.) ---

{\color{Blue}{Skills}} 
& \textbf{Programming} \\
& Python, Racket, C, R, Rust, Java \\
& \\

& \textbf{Languages} \\
& English (fluent), Chinese (basic) \\
& \\

% --- Section: Service and outreach ---

\color{Blue}{Service and outreach}
& \textbf{Director of Marketing and Technology, StarHacks} \hfill Sep. 2020 -- Jan. 2022 \\
& StarHacks is an international non-profit striving to create gender-inclusive spaces in computer science, breaking the stereotype of what it means to be a coder one hackathon at a time. \\
& \\

& \textbf{Director of Marketing, nwPlus} \hfill Sep. 2021 -- Mar. 2022 \\
& nwPlus is a student-led club supporting aspiring programmers and designers, based out of University of British Columbia. \\
& \\

& \textbf{Mentor, connect-f (nwPlus)} \hfill Jul. 2020 -- Apr. 2021 \\
& A mentorship program for girls* in tech designed to pair high school students with university students and new grad mentors.  \\
& \\

% --- End of CV! ---

\end{longtable}
\end{document}
