\section{Research Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://www.ubcigem.com/}{UBC iGEM}}{Nov. 2022 - current}
{Dry Lab Co-Lead and Wiki Lead}{Vancouver, Canada}
\resumeItemListStart
\resumeItem{Leading a team of 6 members to develop innovative models and tools to aid research in a synthethic biology context.}
\resumeItem{Championed and implemented an {\OpenSansBold{\href{https://ubc-igem.github.io/internal-wiki-2023-24/index.html}{internal documentation system}}} for all members to promote knowledge sharing, team transparency and iterative steps towards the success of our project.}
\resumeItem{For 2022/23 season, modeled the {\OpenSansBold{\href{https://2023.igem.wiki/ubc-vancouver/model}{thermodynamics of a StayGold intein-protein}}} folding in aqueous solution, confirming the wet lab results that protein folding was not thermodynamically favored in aqueous solution.}
\resumeItem{Single-handedly developed the {\href{https://gitlab.igem.org/2023/ubc-vancouver}{project wiki, required for the project to be judged.}}}
\resumeItem{{\OpenSansItalic Skills:} Python, SSGs, GROMACS, PyMol, Pyrosetta, HPC, Bash, literature review}
\resumeItemListEnd


\resumeSubheading
{\href{http://www.proofcentre.ca/}{PROOF (Prevention of Organ Failure) Centre of Excellence}}{Jan. 2021 - May 2021}
{Undergraduate NLP Researcher}{Vancouver, Canada}
\resumeItemListStart
\resumeItem{Re-implemented a fragile and nongeneralizable natural language processing pipeline to generate a specific algorithm that can extract patient information from any type of clinical note with any set of labels}
\resumeItem{Added pre-trained word embeddings, generalizable regular expressions, and an OCR correction algorithm to the pipeline, achieving a validation set accuracy of {\OpenSansBold 91\%} on 100 unseen clinical notes}
\resumeItem{Published paper as second author: Chen, Y., Hao, L., Zou, V.Z. {\OpenSansItalic et al.}
	{\href{https://doi.org/10.1186/s12874-022-01583-z}{Automated medical chart review for breast cancer outcomes research: a novel natural language processing extraction system.}}
		{\OpenSansItalic BMC Med Res Methodol 22}, 136 (2022)}
\resumeItem{{\OpenSansItalic Skills:} Python, regular expressions, scispaCy, pandas, Natural Language Processing, Unix, GUI, literature review}
\resumeItemListEnd

\resumeSubHeadingListEnd


